A hierarchical approach for modelling X-ray beamlines. Application to a coherent beamline.

### 2019-05-07 paper-hierarchical.tex
Updates from Overleaf

The very long  source-{\color{green}\sout{sample} optics} distance combined with a small source (in particular for EBS) makes this beamline suitable for experimental techniques requiring a highly coherent beam. Indeed, it has been shown that the clipping of the beam, mainly due to the acceptance of the KB mirrors produces a significant broadening of the focal spot.  As discussed in Section~\ref{level0}, very simple calculation of the diffraction limit can be done using a convergent spherical beam clipped by a slit of 400$\times$400$ \mu$m$^2$ placed  5cm upstream the focus (at the second KB mirror position). The slit vertical size corresponds roughly to the horizontal acceptance of the seconf KB mirror, and it is approximately the same in vertical. A simple simulation of diffraction by a square slit using OASYS is shown in Fig.~\ref{wofry400um}. It reveals a spot of less than 10 nm, thus confirming the analytical predictions, and qualifying this beamline to be a diffraction limited beamline.

@@

We perform here a simplified wavefront simulation in 1D, thus separating the simulations of the horizontal and vertical planes. The source can be simplified by using a point source (spherical wavefront) and applying a Gaussian intensity profile with $\sigma=\sigma'_u d$ with $\sigma'_u$ given by Eq.~\ref{eq:photon small sigmas} and $d$ the distance from the point source to the observation plane. Each optical element can be simplified by separating its action in two parts: the focusing behaviour implemented as an ideal lens, and the finite size because of the boundaries, implemented as a slit. The WOFRY package in OASYS permits to do this work, and it is possible to arrive to a satisfactory result in a few iterations. The beam size at different positions of the beamline are shown in Table~\ref{tablewofry1D}. The final image profiles are in Fig.~\ref{wofry1D}.

@@

A next step in the wave optics simulation is, maintaining the full coherence, to generate a 2D source wavefront that matches in detail the real source (an undulator in a storage ring) and then simulate the propagation of such a wavefront through the optical elements with models that match well the characteristics of the real elements. The source simulated is the on-axis-single-electron emission from the U18.3 undulator tuned to its first harmonic at $E=17225$ eV. The emission by a single-electron is fully coherent. Once the source is defined, one has to go around on how to simulate the beamline optical elements. Increasing the complexity of the simulations one can: a) use ideal thin lenses preceded by slits to emulate finite aperture (as done in the 1D model presented in Section~\ref{wofry}); or b) use grazing incidence focusing optics models \cite{Canestrari2014}. On the top of that, one can add the effect of imperfect optics to the simulations, i.e. slope errors.

The computer code chosen for these calculations is Synchrotron Radiation Workshop (\textsc{srw}) \cite{codeSRW}, which over the past two decades has been extensively benchmarked throughout different synchrotron radiation facilities and has become widely accepted within the X-ray community. Figure \ref{fig:SingleElectron} shows the horizontal integrated intensity at the focal position for the ID16A. It can been seen that there is little difference between using thin ideal lenses or the elliptical mirror model. The elliptical mirror presents a slight reduction in intensity and asymmetry but no significant difference is found, which is in accordance with what is reported in \cite{Canestrari2014}. Notice that the differences are minimal and to remark them we have chosen log plots to represent the intensity distributions at the focal position. It is also important to mention that this equivalency between ideal lenses and elliptical mirrors is only valid at the focal position vicinity: down- or upstream the focal position, differences are not negligible \cite{Canestrari2014}.

It is also possible to add slope errors to the simulations to study the degradation on the focal spot quality (Fig.~\ref{fig:SingleElectron}). For that, the available available metrology data (see Appendix \ref{appendix:metrology})  are used. For both cases (i.e., simulating the beamline using thin optical elements or elliptical mirrors), the beam sizes calculated as the FWHM at the focal position are little affected by the presence of the slope errors (see Table \ref{tab:SRW_results}). There is a significant reduction and shuffling of the interference fringes observed with no slope error. They are almost cancelled, with is an important raise of the background level: the radiation found on the main lobe (focus) shifts to the side lobes when the slope errors are considered. This is accompanied by an obvious reduction on the peak intensity. Table \ref{tab:SRW_results} compiles the beam sizes at focal position for mentioned simulations.

\begin{figure}
    \centering
        \includegraphics[width=4.25cm]{GRAPHICS/se_idealTE_idealOE_h.pdf}
        \includegraphics[width=4.25cm]{GRAPHICS/ebs_slopeTE_slopeOE_h.pdf}
    \label{fig:SingleElectron}
    \caption{Wavefront propagation from a single electron emission through the ID16A beamline. Left: the perfect focusing with ideal lenses (black) is compared with the focusing using elliptical mirrors (red). Right: the same as in the previous plot, but adding the effect of the mirrors slope errors in bothe cases.}
    %Simulations took less than one minute in a desktop computer Intel Core i7 with 8Gb of RAM memory.}
\end{figure}

@@

\subsubsection{Full wave optics simulation: partial coherent case by means of multielectron Monta Carlo sampling}
\label{srw_me}
The wavefront propagation methodology is based in the sampling of a single wavefront (monochromatic and coherent) in a 2D space (in horizontal and vertical spatial dimensions) at a given point of the beamline. This initial point considered as source cannot be the source physical position, because i) when condidering point or spherical waves all the intensity would come in a single pixel so the wavefront is ill-defined, ii) when using synchrotron sources (i.e., undulators) theory \cite{jackson} permits the calculation of the radiation in positions far from the electron trajectory. The limitation of the method is that one wavefront is not representative for a beam that, in storage rings, is produced by the emission of many electrons circulating through the corresponding magnet structure. Diffraction limited sources would emit radiation that can be described in good approximation by a single wavefront. But even for new ultra low-emittance storage rings (improperly called diffraction-limited sources, see discussion in \cite{arxivCF}) the contribution of the electron dimensions ($\sigma_{e(h,v)}$ and $\sigma'_{e(h,v)}$) is not negligeable as compared with the natural emission of radiation ($\sigma_u$ and $\sigma'_u$ for undulators as in Eq.~\ref{eq:photon small sigmas}). To account for this effect one should complete or extend the wavefront simulations to take into account that in fact not only a single wavefront contributes to the properties of the beam. There are three approaches currently used: 1) use of convolutions, 2) Monte Carlo multi-electron sampling, and 3) Propagation of coherent modes. The convolution method consist in calculating the emission characteristics and then convolve the resulting intensity with Gaussians describing the electron beam. This method is simple and fast, as only requires simulation of a single wavefront. However, it presents two important limitations: i) it can only be applied to the intensity calculations and not to other parameters of interest for describing coherence, such as degree of coherence, etc., and ii) it can be applied only at the source position: it is usually unknown how the different optical elements will affect the source contribution to the phase space. The next method, the Monte Carlo multi-electron propagation, it is an statistical method based on the idea that one can exactly calculate the emission and its propagation for one electron that is deterministically described by its initial conditions at the entrance of the magnetic structure. It is therefore possible to perform many simulations for different initial conditions of the travelling electron and make the propagation along the beamline until the observation plane. Then one can statistically combine the different wavefronts (one for each electron) to obtain a sampling of the intensity and other magnitudes useful to describe partially coherent beams. This method presents two difficulties. One is convergence. One cannot know a priori how many electrons must be sampled to obtain a given level of accuracy. The second is computing resources. The emission of each electron must be calculated at the source level, propagated along every element of the beamline, and the resulting wavefront must be analyzed to extract the information to be scored and stored. The third method, the propagation of coherent modes wil be discussed in the next section.

@@

The same observations made on the previous section (full coherent simulations) are pertinent here: there is a reduction on peak intensity when comparing single lens model with the elliptical mirror. The beam sizes and shapes are similar at the focal position, only.

@@

A theoretical study and a numerical algorithm for the coherent mode decomposition of undulator emission in storage rings has been recently proposed  \cite{GlassThesis,GlassEPL} and is implemented in the computer package COMSYL \cite{codeCOMSYL}. The innovative concept is the numerical description of the undulator CSD in terms of its coherent modes $\Phi_m(x,y;z,\omega)$ and eigenvalues $\lambda_m $. One can define the occupation of the coherent modes as
\begin{equation}
 d_m = \frac{\lambda_m}{\sum\limits_{i=0}^{\infty} \lambda_i},
\end{equation}
or the cumulated occupation like
\begin{equation}
 c_m = \sum\limits_{i=0}^{m} d_i.
\end{equation}
An important property of the coherent mode decomposition is that it optimizes the representation of the CSD when the series is truncated. In other words, truncating the series in Eq.~\ref{decomposition} up to the term $m$, the CSD obtained approximates better the exact CSD (this with infinite terms) than any other expansion. It also imply that the first term is more important than the second, and so on. The first or lower term (index zero) is the most important coherent mode. It permits to define the coherent fraction (CF) as the occupation of the lower coherent mode: CF=$d_0$. Obviously, a pretty coherent source will require less modes than a mostly incoherent source to arrive up to a certain representation of the CSD.

We performed COMSYL calculations for the U18.3 undulator radiation of ID16A of 1.4 m length using both the EBS and ESRF-High$\beta$ lattices. The obtained CF are 2.8\% for EBS and 0.13\% for ESRF-High$\beta$, indicating that the overall coherent flux emitted by EBS will be about 20 times the existing coherent flux with ESRF-High$\beta$. Fig.~\ref{fig:histomodes}a shows the cumulated occupation of the coherent modes for the full central cone undulator emission. It shows that the EBS cumulated occupation grows very steply with the number of coherent modes, whereas for ESRF the number of coherent modes needed to attain a given value of cumulated occupation much higher. This can also be shown in Fig.\ref{fig:histomodes}b, where the number of modes to fill 50\%, 75\% and 95\% of spectral density are compared for EBS and ESRF.

@@

The spectral density at the EBS photon source is represented in Fig.~\ref{fig:spectraldensity}a. It shows an elliptical shape with horizontal size larger than the vertical.  The spectral density is reproduced by the addition of the coherent modes weighted by the eigenvectors (from Eq.~\ref{decomposition})
\begin{equation}
S(x,y) = \sum_{m=0}^{\infty} \lambda_m |\Phi_m(x,y)|^2.
\end{equation}
Figs.~\ref{fig:spectraldensity}b-e represent the coherent modes with $m$=0 to $m$=3. It can be shown that the first mode is centered on the axis but extends over an spatial region smaller than the spectral density. Next mode ($m$=1) contributes to extend the spectral density in horizontal, but presents zero intensity at the origin. Successive modes extend  the spectral density in horizontal, sometimes presenting a lobe centerer at zero and sometimes not (e.g., $m$=3). Modes with several lobes along the vertical will also appear, but not so often than in the horizontal, because of the elliptical shape of the spectral density. The coherent modes are orthonormal, thus verifying 
\begin{equation}\label{eq:mode normalization}
M_{mn} = \int_{-\infty}^{\infty} \Phi^*_m(x,y) \Phi_n(x,y)~dx~dy = \delta_{mn}
\end{equation}
with $\delta_{mn}$ the Kronecker delta. The coherence fraction of 2.8\% for the EBS source means that for an optimal coherence experiment one should remove 97.2\% of the emitted photons. This task is performed by the beamline. The beamline elements modify the different modes in a different manner, but it will never be possible to remove all the photons except from the lowest coherent mode, because there is an overlapping of the intensity of the lowest mode with the other ones. Therefore it is impossible to obtain a fully coherent beam that must contain only a single mode.

@@

The coherent modes calculated at the EBS source have been propagated using a beamline simplified with ideal focusing elements and slits to determine their numerical aperture (like in Section~\ref{wofry}). Fig.~\ref{fig:mode transmission} shows how the intensity of the first modes is reduced by geometrical considerations. 
%We recall that in the coherent mode expansion, the modes are orthonormal, therefore the integrated intensity for any mode is always one at the source. 
As discussed, coherent modes will be ``cut'' in a different manner, depending on the slits cropping effect.
This imply that the Eq.~\ref{eq:mode normalization} is not longer verified, and for the propagated modes $M_{mm}\le$1 and $M_{mn}\ne$0 for $m\ne n$. Therefore, the coherent modes of the source after propagation and cropping by the beamline are no longer coherent modes of the resulting beam. Fig.~\ref{fig:mode transmission} shows that the most important transfer ratio ($M_{mm}$)transfer for the lowest mode is about $M_{00}$=25\%, then $M_{22}$=10\% and $M_{44}$=6\%. The other modes shown transfer less than 5\% transfer, and modes higher than $m$=10 practically do not contribute to the final spectral density. Note that, as discussed before, the transmission of mode $m$=2 is higher than mode $m$=1, because this one does not contain a central lobe (Fig.~\ref{fig:spectraldensity}c).

@@

This analysis of the mode transmission is mode dramatic if one looks to the total intensity in the mode, which is given by its eigenvalue. Neglecting modes higher than 10, the lowest coherent mode ($m$=0) carries the 49.5\% of the beam intensity, 18.4\% for the mode $m$=2, and less than 5\% for the others.

>>>>

The very long  source-{\color{green}\sout{sample} optics} distance combined with a small source (in particular for EBS) makes this beamline suitable for experimental techniques requiring a highly coherent beam. Indeed, it has been shown that the clipping of the beam, mainly due to the acceptance of the KB mirrors produces a significant broadening of the focal spot.  As discussed in Section~\ref{level0}, very simple calculation of the diffraction limit can be done using a convergent spherical beam clipped by a slit of 400$\times$400$ \mu$m$^2$ placed  5cm upstream of the focus (at the second KB mirror position). The slit vertical size corresponds roughly to the horizontal acceptance of the second KB mirror, and it is approximately the same in vertical. A simple simulation of diffraction by a square slit using OASYS is shown in Fig.~\ref{wofry400um}. It reveals a spot of less than 10 nm, thus confirming the analytical predictions, and qualifying this beamline to be a diffraction-limited beamline.

@@

We perform here a simplified wavefront simulation in 1D, thus separating the simulations of the horizontal and vertical planes. The source can be simplified by using a point source (spherical wavefront) and applying a Gaussian intensity profile with $\sigma=\sigma'_u d$ with $\sigma'_u$ given by Eq.~\ref{eq:photon small sigmas} and $d$ the distance from the point source to the observation plane. Each optical element can be simplified by separating its action in two parts: the focusing behaviour implemented as an ideal lens, and the finite size because of the boundaries, implemented as a slit. The WOFRY package in OASYS permits such simulations, and it is possible to achieve satisfactory results in a few caluclation iterations. The beam size at different positions of the beamline are shown in Table~\ref{tablewofry1D}. The final image profiles are in Fig.~\ref{wofry1D}.

@@

A next step in the wave optics simulation is, {\color{green}\sout{maintaining the} assuming} full coherence, to generate a 2D source wavefront that matches in detail the real source (an undulator in a storage ring) and then simulate the propagation of such a wavefront through the optical elements with models that match well the characteristics of the real elements. The source simulated is the on-axis-single-electron emission from the U18.3 undulator tuned to its first harmonic at $E=17225$ eV. The emission by a single-electron is fully coherent. Once the source is defined, an approach of how best to simulate the beamline optical elements. Increasing the complexity of the simulations one can: a) use ideal thin lenses preceded by slits to emulate finite apertures (as done in the 1D model presented in Section~\ref{wofry}); or b) use grazing incidence focusing optics models \cite{Canestrari2014}. Furthermore, one can introduce the effect of imperfect optics to the simulations, i.e. slope/figure errors.

The computer code chosen for these calculations is Synchrotron Radiation Workshop (\textsc{srw}) \cite{codeSRW}, which over the past two decades has been extensively benchmarked throughout different synchrotron radiation facilities and has become widely accepted within the X-ray community. Figure \ref{fig:SingleElectron} shows the horizontal integrated intensity at the focal position for the ID16A. It can been seen that there is little difference between using thin ideal lenses or the elliptical mirror model. The elliptical mirror presents a slight reduction in intensity and asymmetry but no significant differences are observed, which is in accordance with  the findings of \cite{Canestrari2014}. Notice that the differences are minimal and to accentuate them we have chosen logarithmically scaled plots to represent the intensity distributions at the focal position. It is also important to mention that this equivalency between ideal lenses and elliptical mirrors is only valid close to the focal position: down- or upstream the focal position, differences are no longer negligible \cite{Canestrari2014}.

It is also possible to add slope errors to the simulations to study the resulting impact upon the focal spot quality (Fig.~\ref{fig:SingleElectron}). For that, the available surface metrology data of the reflective elements (see Appendix \ref{appendix:metrology})  are used. For both cases (i.e., simulating the beamline using thin optical elements or elliptical mirrors), the beam sizes calculated as the FWHM at the focal position are little affected by the presence of the slope errors (see Table \ref{tab:SRW_results}). There is a significant reduction and {\color{green}\sout{shuffling} blurring} of the interference fringes compared to observations with no slope error. They are almost completely removed and associated with a large increase of the background level: the radiation found on the main lobe (focus) shifts to the side lobes when the slope errors are considered. This is accompanied by an obvious reduction on the peak intensity. Table \ref{tab:SRW_results} compiles the beam sizes at focal position for mentioned simulations.

\begin{figure}
    \centering
        \includegraphics[width=4.25cm]{GRAPHICS/se_idealTE_idealOE_h.pdf}
        \includegraphics[width=4.25cm]{GRAPHICS/ebs_slopeTE_slopeOE_h.pdf}
    \label{fig:SingleElectron}
    \caption{Wavefront propagation from a single electron emission through the ID16A beamline. Left: the perfect focusing with ideal lenses (black) is compared with the focusing using elliptical mirrors (red). Right: the same as in the previous plot, but adding the effect of the mirrors slope errors in both cases.}
    %Simulations took less than one minute using a desktop computer Intel Core i7 with 8Gb of RAM memory.}
\end{figure}

@@

\subsubsection{Full wave optics simulation: partial coherent case by means of multielectron Monte Carlo sampling}
\label{srw_me}
The wavefront propagation methodology is based in the sampling of a single wavefront (monochromatic and coherent) in a 2D space (in horizontal and vertical spatial dimensions) at a given point of the beamline. This initial point considered as source cannot be the source physical position, because i) when considering point or spherical waves all the intensity would be concentrated in a single pixel so the wavefront is ill-defined, ii) when using synchrotron sources (i.e., undulators) theory \cite{jackson} permits the calculation of the radiation in positions far from the electron trajectory. The limitation of the method is that one wavefront is not representative for a beam that, in storage rings, is produced by the emission of many electrons circulating through the corresponding magnet structure. Diffraction limited sources would emit radiation that can be described in good approximation by a single wavefront. But even for new ultra low-emittance storage rings (improperly called diffraction-limited sources, see discussion in \cite{arxivCF}) the contribution of the electron dimensions ($\sigma_{e(h,v)}$ and $\sigma'_{e(h,v)}$) is not negligeable as compared with the natural emission of radiation ($\sigma_u$ and $\sigma'_u$ for undulators as in Eq.~\ref{eq:photon small sigmas}). To account for this effect one should complete or extend the wavefront simulations to take into account that in fact not only a single wavefront contributes to the properties of the beam. There are three approaches currently used: 1) use of convolutions, 2) Monte Carlo multi-electron sampling, and 3) Propagation of coherent modes. The convolution method consists of calculating the emission characteristics and then convolving the resulting intensity with Gaussians describing the electron beam. This method is simple and fast, as only requires simulation of a single wavefront. However, it presents two important limitations: i) it can only be applied to the intensity calculations and not to other parameters of interest for describing coherence, such as degree of coherence, etc., and ii) it can be applied only at the source position: it is usually unknown how the different optical elements will affect the source contribution to the phase space. The next method, the Monte Carlo multi-electron propagation,  is a statistical method based on the idea that one can exactly calculate the emission and its propagation for one electron that is deterministically described by its initial conditions at the entrance of the magnetic structure. It is therefore possible to perform many simulations for different initial conditions of the travelling electron and make the propagation along the beamline until the observation plane. Then one can statistically combine the different wavefronts (one for each electron) to obtain a sampling of the intensity and other magnitudes useful to describe partially coherent beams. This method presents two difficulties. One is convergence. One cannot know a priori how many electrons must be sampled to obtain a given level of accuracy. The second is computing resources. The emission of each electron must be calculated at the source level, propagated along every element of the beamline, and the resulting wavefront must be analyzed to extract the information to be scored and stored. The third method, the propagation of coherent modes wil be discussed in the next section.

@@

The same observations made in the previous section (fully coherent simulations) are pertinent here: there is a reduction of the peak intensity when comparing simple lens model with the elliptical mirror. The beam sizes and shapes are similar at the focal position, only.
{\todo{more detailed comments on comparisons with filament beam results? For comparison also information on calculation time, number of electrons, ...}}

@@

A theoretical study and a numerical algorithm for the coherent mode decomposition of undulator emission in storage rings has been recently proposed  \cite{GlassThesis,GlassEPL} and is implemented in the computer package COMSYL \cite{codeCOMSYL}. The innovative concept is the numerical description of the undulator CSD in terms of its coherent modes $\Phi_m(x,y;z,\omega)$ and eigenvalues $\lambda_m $. One can define the occupation of the coherent modes as
\begin{equation}
 d_m = \frac{\lambda_m}{\sum\limits_{i=0}^{\infty} \lambda_i},
\end{equation}
or the cumulated occupation like
\begin{equation}
 c_m = \sum\limits_{i=0}^{m} d_i.
\end{equation}
An important property of the coherent mode decomposition is that it optimizes the representation of the CSD when the series is truncated. In other words, truncating the series in Eq.~\ref{decomposition} up to the term $m$, the CSD obtained approximates better the exact CSD (this with infinite terms) than any other expansion. It also implies that the first term is more important than the second, and so on. The first or lower term (index zero) is the most important coherent mode. It permits definition of the coherent fraction (CF) as the occupation of the lower coherent mode: CF=$d_0$. Obviously, a more coherent source will require less modes than a mostly incoherent source to approximate the CSD to a given precision.

We performed COMSYL calculations for the U18.3 undulator radiation of ID16A of 1.4 m length using both the EBS and ESRF-High$\beta$ lattices. The obtained CF are 2.8\% for EBS and 0.13\% for ESRF-High$\beta$, indicating that the overall coherent flux emitted by EBS will be about 20 times the existing coherent flux with ESRF-High$\beta$. Fig.~\ref{fig:histomodes}a shows the cumulated occupation of the coherent modes for the full central cone undulator emission. It shows that the EBS cumulated occupation grows very steeply with the number of coherent modes, whereas for ESRF the number of coherent modes needed to attain a given value of cumulated occupation much higher. This can also be shown in Fig.\ref{fig:histomodes}b, where the number of modes to fill 50\%, 75\% and 95\% of spectral density are compared for EBS and ESRF.

@@

The spectral density at the EBS photon source is represented in Fig.~\ref{fig:spectraldensity}a. It shows an elliptical shape with horizontal size larger than the vertical.  The spectral density is reproduced by the addition of the coherent modes weighted by the eigenvectors (from Eq.~\ref{decomposition})
\begin{equation}
S(x,y) = \sum_{m=0}^{\infty} \lambda_m |\Phi_m(x,y)|^2.
\end{equation}
Figs.~\ref{fig:spectraldensity}b-e represent the coherent modes with $m$=0 to $m$=3. It can be shown that the first mode is centered on the axis but extends over a spatial region smaller than the spectral density. The next mode ($m$=1) contributes to extend the spectral density in horizontal, but presents zero intensity at the origin. Successive modes extend  the spectral density in horizontal, sometimes presenting a lobe center at zero and sometimes not (e.g., $m$=3). Modes with several lobes along the vertical will also appear, but not so often than in the horizontal, because of the elliptical shape of the spectral density. The coherent modes are orthonormal, thus verifying 
\begin{equation}\label{eq:mode normalization}
M_{mn} = \int_{-\infty}^{\infty} \Phi^*_m(x,y) \Phi_n(x,y)~dx~dy = \delta_{mn}
\end{equation}
with $\delta_{mn}$ the Kronecker delta. The coherence fraction of 2.8\% for the EBS source means that for an optimal coherence experiment one should remove 97.2\% of the emitted photons. This task is performed by the beamline. The beamline elements modify the different modes in a different manner, but it will never be possible to remove all the photons except from the lowest coherent mode, because there is an overlapping of the intensity of the lowest mode with the other ones. Therefore it is impossible to obtain a fully coherent beam containing only a single mode.

@@

The coherent modes calculated at the EBS source have been propagated \todo{Using which propagation code - is this all in COMSYL?} using a simplified beamline  with ideal focusing elements and slits to determine their numerical aperture (like in Section~\ref{wofry}). Fig.~\ref{fig:mode transmission} shows how the intensity of the first modes is reduced by geometrical considerations. 
%We recall that in the coherent mode expansion, the modes are orthonormal, therefore the integrated intensity for any mode is always one at the source. 
As discussed, coherent modes will be ``cut'' in a different manner, depending on the slits aperturing effect.
This implies that the Eq.~\ref{eq:mode normalization} is not longer {\color{green}\sout{verfified} satisfied}, and for the propagated modes $M_{mm}\le$1 and $M_{mn}\ne$0 for $m\ne n$. Therefore, the coherent modes of the source after propagation and cropping by the beamline are no longer coherent modes of the resulting beam. Fig.~\ref{fig:mode transmission} shows that the most important transfer ratio ($M_{mm}$)transfer for the lowest mode is about $M_{00}$=25\%, then $M_{22}$=10\% and $M_{44}$=6\%. The other modes shown transfer less than 5\% transfer, and modes higher than $m$=10 practically do not contribute to the final spectral density. Note that, as discussed before, the transmission of mode $m$=2 is higher than mode $m$=1, because this one does not display a central lobe (Fig.~\ref{fig:spectraldensity}c).

@@

This analysis of the mode transmission is more dramatic if one looks at the total intensity in the mode, which is given by its eigenvalue. Neglecting modes higher than 10, the lowest coherent mode ($m$=0) carries the 49.5\% of the beam intensity, 18.4\% for the mode $m$=2, and less than 5\% for the others.
